---
title: "DDM_Pre20_FOI"
author: "Aubrey Condor"
date: "3/5/2021"
output: html_document
---
### 1. FOI (Formal Inference) Construct Map
<a href="https://cr4cradmin.bear-apps.com/constructs/public/DQvEDPYILUHsRbPTCHIPyyyN8IYoP8" target = "_blank">Link </a> to construct map

### 2. Items & Scoring Guides
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/weXzb8u61TRvgPwkkgzzYAzxs11KFM" target ="_blank"> Pvalue.01_MC </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/6KBGU3NrTs8Jtq92fdAE3Zzi5FS85l" target = "_blank">Helpline.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/NUbbhreoju54qLwU2YjPXIQSrXC3n2" target = "_blank">Cats.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/8Q5Uo5KwMZZPY7wKbDtDkpiutZuVEH" target = "_blank">Literature.02_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/kXvdgVdrOIB6sHGtOaBONVoNeNX69t" target = "_blank">Literature.03_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/EIO4QgBsgs1KHxdi5dvht8lV8O1oJX" target = "_blank">GuineaPig.04_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/P2z9yUgMdeEoqDQlCyy3pb3lADmuod" target = "_blank">DogDiet.01_MCOE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/8UpS7I6oRvzuenQht6MfaexfwsNU8B" target = "_blank">MPG.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/sCLh7TTiO6dfxypQ8CiVhNPSTzW9sF" target = "_blank">MPG.02_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/iCj1kerwNnz85ZrN8pcBwHzJhjfZiG" target = "_blank">WebClicks.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/5ZbOMXvO4HkvYmo76ivjRKsaCMYar1" target = "_blank">Chocolate.04_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/btnZLJtfquFEg491EVIi1Fz1312RYk" target = "_blank">Chocolate.05_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/UNe382WmSpEMu8xlZ63Qh187FbyHtl" target = "_blank">Chocolate.01b03_MCMC  </a>




```{r setup, include=FALSE}
library(TAM)
library(dplyr)
library(WrightMap)
setwd("C:/Users/condo/PycharmProjects/NMSI_stat")

# change file depending on the construct
##############################################################################
raw_resp <- read.csv("R_UMV.csv")
##############################################################################

resp <- raw_resp[!!rowSums(!is.na(raw_resp)),]
resp <- lapply(resp, as.numeric)
resp <- as.data.frame(resp)

mod1 <- tam(resp)
item_param <- mod1$xsi$xsi #item parameters
item_thresh <- tam.threshold(mod1) #thurst thresholds
summary(mod1) # summary of the model

pers_abil <- mod1$person$EAP

item_thresh['CuppaJoe.04_MC', 1] <- NA
item_thresh['GuineaPig.01_MC', 1] <- NA
item_thresh['Inventions.03ab_MCMC', 1] <- NA
item_thresh['Inventions.04a_MConly', 1] <- NA
item_thresh['Inventions.01_MC', 1] <- NA
item_thresh['MMpacket.01ab_OE', 1] <- NA
item_thresh['GuineaPig.02_MC', 1] <- NA
item_thresh['PopSongs.01_MC', 2] <- NA

#View(LDC_thresh)
# add col names for LDC_thresh df
#colnames(item_thresh) <- c("item", "L1", "L2 ", "L3", "L4")
#get rid of item col for WrightMap 1
#thresh4wm1 <- item_thresh %>% select(-item)
# transposing item_thresh for WM2
library(tidyr)
#transposing item_thresh to tt for Wright map #2 w/thresholds on x-axis   
#tt <- item_thresh %>%
#  gather(var, value, -item) %>% 
#  spread(item, value) 
#dim(tt) # 4 x 14
# drop the first column
#tt <- tt[(1:4), (2:14)]
# x-axis labels for Wright map #2
#itemnames2 <- c("L0 vs.L1", "L1 vs.L2", "L2 vs.L3", "L3 vs.L4")
#colors for Wright map #2
#itemcolors <- c("#D7191C", "#2B83BA", "forestgreen", "blueviolet")
#color code categories
#ncat <- ncol(thresh4wm1)
#nitems <- nrow(thresh4wm1)
#itemlevelcolors <- matrix(rep( RColorBrewer::brewer.pal(ncat, "Set1"), nitems), byrow=TRUE, ncol=ncat)
```

### 3. Wright Maps

```{r plots, echo=FALSE, results = FALSE, fig.keep = 'all', message = FALSE, warning = FALSE, fig.align = "center"}
#Wright map #1 (items on x-axis)
library(RColorBrewer)
ncat <- 5
I <- ncol(mod1$resp)
itemlevelcolors <- matrix(rep( RColorBrewer::brewer.pal(ncat, "Set1"), I),
                           byrow=TRUE, ncol=ncat)

wrightMap(pers_abil, item_thresh, thr.sym.col.fg=itemlevelcolors,
          thr.sym.col.bg=itemlevelcolors,label.items.srt=65)
#mean(LDC$p.est$`est (d1)`)
#sd(LDC$p.est$`est (d1)`)
#Wright map #2 (thresh on x-axis)
#wrightMap(item_est, tt,
#          label.items = itemnames2,
#          main.title   = "Wright Map: LDC (by thresholds)",
#          thr.sym.col.fg = itemcolors,
#          thr.sym.col.bg = itemcolors,
#          axis.items = "Threshold")
```

```{r calib.results, echo=FALSE, results = FALSE}
n.cases <- length(resp)
n.items <- dim(item_thresh)[1]
eap.rel <- mod1$EAP.rel
#min.Wfit <- min(LDC$RMP$item$W.fit)
#max.Wfit <- max(LDC$RMP$item$W.fit)
```
#####   Calibration stats

*  `r n.cases` cases (the overall DDM sample is 2,265. Of which, 422 are AP Stats students. 28 students excluded due to answering less than 20% of items; 3 more dropped for unknown reason.)
*  `r n.items` scorable "units"
*  EAP/PV Reliability: `r eap.rel`



#####   Observations

* Birthrate
  + Multi-select item. Seems to be working well.
* Discussion
  + Multi-select with a single correct answer. Seems to be working.
* Paternity
* MPG
  + The most correct choice scored at L4 but should be downgraded to L3.
  + Not sure if partial credit (L2) is needed for this item. 
* Cats
    + Cats.02c very difficult. It asks about sampling method to support a claim. Try polytmous scoring?
*  Twitter
    + Twitter.01 L1 threshold very low: only 5% scored into 0. Should it be dichotomously scored?
    + L3 thresholds are quite low. More like L2s. 
    + Twitter3_MCMC is SR version of Claim + Explanation. Selecting all the "correct" explanations is rare/hard (L4) although selecting a couple (L3) is fairly easy/common.


### 4. Threshold Difficulty
#```{r tables, echo=FALSE, message = FALSE, warning = FALSE}
#knitr::kable(item_thresh, format = "html", digits = 2) %>%
#  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
#                full_width = TRUE, font_size = 12)
```

### 5. Item Analysis
* <a href="https://drive.google.com/file/d/1a3chPFPDbQ2-XYdyFu3kSCwGR9HkPwRC/view?usp=sharing" target = "_blank">Link to Item Analysis </a> (ConQuest output)