---
title: "UMV Pretest Fall 20 Calibration"
author: 
date: "3/9/2021"
output: html_document
toc: true
toc_float: true
---

### 1. UMV (understanding measures of variability) Construct Map
<a href="https://cr4cradmin.bear-apps.com/constructs/public/HxpdvrHpo2zUj65hjNZXyJuheExFSY" target = "_blank">Link </a> to construct map

### 2. Items & Scoring Guides
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/YYVg87Kjz54mnJHea5jPY872MX68pl" target = "_blank">CuppaJoe.01_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/8udfxCj6Kmr9Tjd1HVFk9kxXPHP6H8" target = "_blank">CuppaJoe.03_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/AJKwoSsbWJBhVKPwwLg9hGQWgf65U2" target ="_blank"> CuppaJoe.04_MC </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/81/scoring_guides/151/score_assignments" target = "_blank">DogDiet.02_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/83/scoring_guides/152/score_assignments" target = "_blank">DogDiet.03_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/57/scoring_guides/386/score_assignments" target = "_blank">GuineaPig.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/57/scoring_guides/151/score_assignments" target = "_blank">GuineaPig.02_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/82/scoring_guides/434/score_assignments" target = "_blank">GuineaPig.03_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/59/scoring_guides/340/score_assignments" target = "_blank">Inventions.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/58/scoring_guides/373/score_assignments" target = "_blank">Inventions.03ab_MCMC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/58/scoring_guides/342/score_assignments" target = "_blank">Inventions.04a_MConly  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/5u7fKqr9iksqA4FpON3HlueOVsLRQJ" target = "_blank">MMpacket.01ab_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/WdBVXbKRbnP6rIq2wG2eYvWJaxugJ4" target = "_blank">MMpacket.02ab_NU  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/Z5qxNBXMCyS6hGD3eA7JomNeUenWrc" target = "_blank">MMpacket.03ab_NU  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/ANRqfxKdaNBcLC9RLvMW1621JaxlIW" target = "_blank">MMpacket.04ab_NU  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/juP7IVJnOooBS6Ij6qZK6MVicGlpAD" target = "_blank">MMpacket.05  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/iHUxQhsS82uZjjO3iCf1FAVSBWLLyP" target = "_blank">Painting.01_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/KhXIDs9be4s5tQh1zRO39ajvqPCzG1" target = "_blank">Painting.02_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/oKLQNB287yJLZ3pRAOoKPSySAc7QK2" target = "_blank">PopSongs.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/fxsegyrwwhlmKuy7QEDdY7CBJ33jJM" target = "_blank">PopSongs.01_MCOE  </a>

##### Response choice distributions
* See <a href="https://cr4cradmin.bear-apps.com/answers_reports?scheduled_activities=36" target = "_blank">answers report.  </a> 

```{r setup, include=FALSE}
require(WrightMap)
require(tidyverse)
require(RColorBrewer)
require(knitr)
require(kableExtra)

knitr::opts_chunk$set(echo = TRUE)


#Import ConQuest data
UMV <- CQmodel(p.est = "data/UMV_WLE.txt", show = "data/UMV_SHOW.txt")

#full item names
i.names<-UMV$RMP$item$item
i.names[1,] <- "CupJ.4_MC"
i.names[2,] <- "Invent.4a_MC"
i.names[3,] <- "Invent.3ab_MC2"
i.names[4,] <- "Guinea.1_MC"
i.names[5,] <- "Guinea.3_MC"
i.names[6,] <- "Guinea.2_MC"
i.names[7,] <- "CupJ.1_OE"
i.names[8,] <- "DogDiet.2_MC"
i.names[9,] <- "DogDiet.3_OE"
i.names[10,] <- "Invent.1_MC" 
i.names[11,] <- "Pop.1_MC" 
i.names[12,] <- "Pop.1_MCOE" 
i.names[13,] <- "MM.1ab_OE" 
i.names[14,] <- "MM.5_OE" 
i.names[15,] <- "MM.2ab_NU" 
i.names[16,] <- "MM.3ab_NU" 
i.names[17,] <- "MM.4ab_NU"
i.names[18,] <- "CupJ.3_OE" 
i.names[19,] <- "Paint.2_OE" 
i.names[20,] <- "Paint.1_OE"
itemnames <- sort(i.names)

#thetas
UMV_est<-UMV$p.est$`est (d1)`

#move thresholds for items that skipped levels (by design)
UMV_thresh <- make.thresholds(UMV) %>% 
  as.data.frame()

# mannually adjusting thresholds for skipped levels etc.

# CupJoe4 - L2 --> L3 & L1 --> L2
UMV_thresh[1, 3] <- UMV_thresh[1, 2]
UMV_thresh[1, 2] <- UMV_thresh[1, 1]
UMV_thresh[1, 1] <- NA

# Invent.4a_MC - L1 --> L2
UMV_thresh[2, 2] <- UMV_thresh[2, 1]
UMV_thresh[2, 1] <- NA

# Invent.3ab_MCNC - L2 --> L3 & L1 --> L2
UMV_thresh[2, 3] <- UMV_thresh[2, 2]
UMV_thresh[2, 2] <- UMV_thresh[2, 1]
UMV_thresh[2, 1] <- NA

# GuineaPig.1_MC - L2 --> L3 & L1 --> L2
UMV_thresh[4, 3] <- UMV_thresh[4, 2]
UMV_thresh[4, 2] <- UMV_thresh[4, 1]
UMV_thresh[4, 1] <- NA

# "GuineaPig.2_MC" - L2 --> L3 & L1 --> L2
UMV_thresh[6, 3] <- UMV_thresh[6, 2]
UMV_thresh[6, 2] <- UMV_thresh[6, 1]
UMV_thresh[6, 1] <- NA

# Invent.1_MC L2 --> L3 & L1 --> L2
UMV_thresh[10, 3] <- UMV_thresh[10, 2]
UMV_thresh[10, 2] <- UMV_thresh[10, 1]
UMV_thresh[10, 1] <- NA

# PopSongs.1_MC  L2 --> L3
UMV_thresh[11, 3] <- UMV_thresh[11, 2]
UMV_thresh[11, 2] <- NA

# MMpacket.1ab
UMV_thresh[13, 3] <- UMV_thresh[13, 2]
UMV_thresh[13, 2] <- UMV_thresh[13, 1]
UMV_thresh[13, 1] <- NA

# get item rownames as the first column
UMV_thresh <- UMV_thresh %>% 
  rownames_to_column(., "item")

UMV_thresh <- UMV_thresh %>% arrange(item)

# get the right item names as set above
UMV_thresh$item <- itemnames

UMV_thresh <- UMV_thresh %>% arrange(item) 
#View(UMV_thresh)

# add col names for UMV_thresh df
colnames(UMV_thresh) <- c("item", "L1", "L2 ", "L3", "L4")

#get rid of item col for WrightMap 1
thresh4wm1 <- UMV_thresh %>% select(-item)


# transposing item_thresh for WM2
library(tidyr)
#transposing item_thresh to tt for Wright map #2 w/thresholds on x-axis   
tt <- UMV_thresh %>%
  gather(var, value, -item) %>% 
  spread(item, value) 
dim(tt) # 4 x 21

# drop the first column
tt <- tt[(1:4), (2:21)]

# x-axis labels for Wright map #2
itemnames2 <- c("L0 vs.L1", "L1 vs.L2", "L2 vs.L3", "L3 vs.L4")
#colors for Wright map #2
itemcolors <- c("#D7191C", "#2B83BA", "forestgreen", "blueviolet")

#color code categories
ncat <- ncol(thresh4wm1)
nitems <- nrow(thresh4wm1)
itemlevelcolors <- matrix(rep( RColorBrewer::brewer.pal(ncat, "Set1"), nitems), byrow=TRUE, ncol=ncat)

```

### 3. Wright Maps

```{r plots, echo=FALSE, results = FALSE, fig.keep = 'all', message = FALSE, warning = FALSE, fig.align = "center"}

#Wright map #1 (items on x-axis)
wrightMap(UMV_est, thresh4wm1,
          label.items = itemnames, 
          label.items.srt = 65, 
          thr.sym.col.fg = itemlevelcolors, 
          thr.sym.col.bg = itemlevelcolors,
          show.thr.lab = FALSE,
          vertLines = TRUE,
          axis.items="")

#mean(UMV$p.est$`est (d1)`)
#sd(UMV$p.est$`est (d1)`)

#Wright map #2 (thresh on x-axis)
wrightMap(UMV_est, tt,
          label.items = itemnames2,
          main.title   = "Wright Map: UMV (by thresholds)",
          thr.sym.col.fg = itemcolors,
          thr.sym.col.bg = itemcolors,
          axis.items = "Threshold",
          thr.lab.cex = 0.4)

```

```{r calib.results, echo=FALSE, results = FALSE}
n.cases <- length(UMV_est)
n.items <- length(i.names)
eap.rel <- UMV$rel.coef[[3]]
min.Wfit <- min(UMV$RMP$item$W.fit)
max.Wfit <- max(UMV$RMP$item$W.fit)
```
#####   Calibration stats

*  `r n.cases` cases (the overall DDM sample is 2,265. Of which, 422 are AP Stats students. 28 students excluded due to answering less than 20% of items; 3 more dropped for unknown reason.)
*  `r n.items` scorable "units"
*  EAP/PV Reliability: `r eap.rel`
*  Weighted MNSQ range: `r min.Wfit` - `r max.Wfit`


#####   Observations

*  Highest thresholds: Should these be relabeled as L4?
  + CuppaJoe.01
  + CuppaJoe.03
  + DogDiet.03
  + Inventions.3ab
  + MM.01ab
  + MM.04ab
  + MM.05ab
*  High L1 thresholds: should these be relabeled as L2?
  + DogDiet.02
  + GuineaPig.02 (should this be dicotomously scored? Same applies to GuineaPig3)
  + Inventions.3ab
  + Pop.01_MC
*  Low L4 threshold: Should these be relabeled as L3 and push down the rest?
  + Pop.01_MCOE
  *  Low L3 thresholds: Should these be relabeled as L2?
  + CuppaJoe.04
  + Inventions.01

### 4. Threshold Difficulty
```{r tables, echo=FALSE, message = FALSE, warning = FALSE}

knitr::kable(UMV_thresh, format = "html", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE, font_size = 12)

```

### 5. Item Analysis
* <a href="https://drive.google.com/file/d/1QRlpodAXt9NBtsBO-cHRSWGyaYvv7I1n/view?usp=sharing" target = "_blank">Link to Item Analysis </a> (ConQuest output)   
