---
title: "DDM_Pre20_FOI"
date: "3/5/2021"
output: html_document
---
### 1. FOI (Formal Inference) Construct Map
<a href="https://cr4cradmin.bear-apps.com/constructs/public/DQvEDPYILUHsRbPTCHIPyyyN8IYoP8" target = "_blank">Link </a> to construct map

### 2. Items & Scoring Guides
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/weXzb8u61TRvgPwkkgzzYAzxs11KFM" target ="_blank"> Pvalue.01_MC </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/6KBGU3NrTs8Jtq92fdAE3Zzi5FS85l" target = "_blank">Helpline.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/NUbbhreoju54qLwU2YjPXIQSrXC3n2" target = "_blank">Cats.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/8Q5Uo5KwMZZPY7wKbDtDkpiutZuVEH" target = "_blank">Literature.02_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/kXvdgVdrOIB6sHGtOaBONVoNeNX69t" target = "_blank">Literature.03_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/EIO4QgBsgs1KHxdi5dvht8lV8O1oJX" target = "_blank">GuineaPig.04_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/P2z9yUgMdeEoqDQlCyy3pb3lADmuod" target = "_blank">DogDiet.01_MCOE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/8UpS7I6oRvzuenQht6MfaexfwsNU8B" target = "_blank">MPG.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/sCLh7TTiO6dfxypQ8CiVhNPSTzW9sF" target = "_blank">MPG.02_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/iCj1kerwNnz85ZrN8pcBwHzJhjfZiG" target = "_blank">WebClicks.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/5ZbOMXvO4HkvYmo76ivjRKsaCMYar1" target = "_blank">Chocolate.04_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/btnZLJtfquFEg491EVIi1Fz1312RYk" target = "_blank">Chocolate.05_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/UNe382WmSpEMu8xlZ63Qh187FbyHtl" target = "_blank">Chocolate.01b03_MCMC  </a>


##### Response choice distributions
* See <a href="https://cr4cradmin.bear-apps.com/answers_reports?scheduled_activities=36" target = "_blank">answers report.  </a> 

```{r setup, include=FALSE}
require(WrightMap)
require(tidyverse)
require(RColorBrewer)
require(knitr)
require(kableExtra)

knitr::opts_chunk$set(echo = TRUE)


#Import ConQuest data
FOI <- CQmodel(p.est = "data/FOI_WLE.txt", show = "data/FOI_SHOW.txt")

#full item names
i.names<-FOI$RMP$item$item
i.names[1,] <- "Pval_MC"
i.names[2,] <- "Helpline_MC"
i.names[3,] <- "Cats1_MC"
i.names[4,] <- "Literature2_OE"
i.names[5,] <- "Literature3_OE"
i.names[6,] <- "Guinea4_MC"
i.names[7,] <- "MPG1_MC"
i.names[8,] <- "MPG2_MC"
i.names[9,] <- "Webclicks1_MC"
i.names[10,] <-	"Choco4_OE"
i.names[11,] <-	"Choco5_OE"
i.names[12,] <-	"Choco1b3_MC2" 
itemnames <- sort(i.names)

#thetas
FOI_est<-FOI$p.est$`est (d1)`

#move thresholds for items that skipped levels (by design)
FOI_thresh <- make.thresholds(FOI) %>% 
  as.data.frame() %>% 
  mutate(V4 = NA)

# mannually adjusting thresholds for skipped levels etc.

# Pval - L2 --> L4, L1 --> L3
FOI_thresh[1, 4] <- FOI_thresh[1, 2]
FOI_thresh[1, 3] <- FOI_thresh[1, 1]
FOI_thresh[1, 2] <- NA
FOI_thresh[1, 1] <- NA

# Helpline - L2 --> L4, L1 --> L2
FOI_thresh[2, 4] <- FOI_thresh[2, 2]
FOI_thresh[2, 2] <- FOI_thresh[2, 1]
FOI_thresh[2, 1] <- NA

# Cats - L3 --> L4
FOI_thresh[3, 4] <- FOI_thresh[3, 3]
FOI_thresh[3, 3] <- NA

# MPG1 - L2 --> L3, L1 --> L2
FOI_thresh[7, 3] <- FOI_thresh[7, 2]
FOI_thresh[7, 2] <- FOI_thresh[7, 1]
FOI_thresh[7, 1] <- NA

# MPG2 - L2 --> L3, L1 --> L2
FOI_thresh[8, 3] <- FOI_thresh[8, 2]
FOI_thresh[8, 2] <- FOI_thresh[8, 1]
FOI_thresh[8, 1] <- NA

# Webclick - L2 --> L4, L1 --> L3
FOI_thresh[9, 4] <- FOI_thresh[9, 2]
FOI_thresh[9, 2] <- FOI_thresh[9, 1]
FOI_thresh[9, 3] <- NA
FOI_thresh[9, 1] <- NA

# get item rownames as the first column
FOI_thresh <- FOI_thresh %>% 
  rownames_to_column(., "item")

FOI_thresh <- FOI_thresh %>% arrange(item)

# get the right item names as set above
FOI_thresh$item <- itemnames

View(FOI_thresh)

# add col names for FOI_thresh df
colnames(FOI_thresh) <- c("item", "L1", "L2 ", "L3", "L4", "L5")

#get rid of item col for WrightMap 1
thresh4wm1 <- FOI_thresh %>% select(-item)


# transposing item_thresh for WM2
library(tidyr)
#transposing item_thresh to tt for Wright map #2 w/thresholds on x-axis   
tt <- FOI_thresh %>%
  gather(var, value, -item) %>% 
  spread(item, value) 
dim(tt) # 5 x 10

# drop the first column
tt <- tt[(1:5), (2:10)]

# x-axis labels for Wright map #2
itemnames2 <- c("L0 vs.L1", "L1 vs.L2", "L2 vs.L3", "L3 vs.L4", "L4 vs.L5")
#colors for Wright map #2
itemcolors <- c("#D7191C", "#2B83BA", "forestgreen", "blueviolet", "orange2")

#color code categories
ncat <- ncol(thresh4wm1)
nitems <- nrow(thresh4wm1)
itemlevelcolors <- matrix(rep( RColorBrewer::brewer.pal(ncat, "Set1"), nitems), byrow=TRUE, ncol=ncat)

```

### 3. Wright Maps

```{r plots, echo=FALSE, results = FALSE, fig.keep = 'all', message = FALSE, warning = FALSE, fig.align = "center"}

#Wright map #1 (items on x-axis)
wrightMap(FOI_est, thresh4wm1,
          label.items = itemnames, 
          label.items.srt = 65, 
          thr.sym.col.fg = itemlevelcolors, 
          thr.sym.col.bg = itemlevelcolors,
          axis.items="")

#mean(FOI$p.est$`est (d1)`)
#sd(FOI$p.est$`est (d1)`)

#Wright map #2 (thresh on x-axis)
wrightMap(FOI_est, tt,
          label.items = itemnames2,
          main.title   = "Wright Map: FOI (by thresholds)",
          thr.sym.col.fg = itemcolors,
          thr.sym.col.bg = itemcolors,
          axis.items = "Threshold")

```

```{r calib.results, echo=FALSE, results = FALSE}
n.cases <- length(FOI_est)
n.items <- length(i.names)
eap.rel <- FOI$rel.coef[[3]]
min.Wfit <- min(FOI$RMP$item$W.fit)
max.Wfit <- max(FOI$RMP$item$W.fit)
```
#####   Calibration stats

*  `r n.cases` cases (the overall DDM sample is 2,265. Of which, 422 are AP Stats students. 28 students excluded due to answering less than 20% of items; 3 more dropped for unknown reason.)
*  `r n.items` scorable "units"
*  EAP/PV Reliability: `r eap.rel`
*  Weighted MNSQ range: `r min.Wfit` - `r max.Wfit`


#####   Observations

* Swim2_MC: The most difficult item. Frequency on the y-axis might be an appealing distractor. Better to be labeled as "number of respondents"?
* Swim1_MC: Very easy as only two options are plausible.
* Invent7's L3 appears to be more like Level 4.
* AirQuality and GPA are parallel items but L2 and L3 locations are somewhat different. 
* Birthday & Invent89 have a nice spread among the thresholds, while Titanic1b's thresholds are all squished. 

### 4. Threshold Difficulty
```{r tables, echo=FALSE, message = FALSE, warning = FALSE}

knitr::kable(FOI_thresh, format = "html", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE, font_size = 12)

```

### 5. Item Analysis
* <a href="https://drive.google.com/file/d/1gaKwS-sWlXFbEKZlkMs9fg9ZuFWGvADp/view?usp=sharing" target = "_blank">Link to Item Analysis </a> (ConQuest output)   