---
title: "MRC Pretest Fall 20 Calibration"
author: 
date: "2/25/2021"
output: html_document
toc: true
toc_float: true
---

### 1. MRC (meta representational competence) Construct Map
<a href="https://docs.google.com/presentation/d/1NjSoUVslENGustXvAMzPBNxeMjYsbh6QRWoLzQygG74/edit#slide=id.gc115133d65_0_9" target = "_blank">Link </a> to construct map

### 2. Items & Scoring Guides
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/56/scoring_guides/426/score_assignments" target ="_blank"> AirQuality1_MC 
</a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/58/scoring_guides/685/score_assignments" target = "_blank">Birthday1_MCOE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/60/scoring_guides/379/score_assignments" target = "_blank">Invent7_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/60/scoring_guides/506/score_assignments" target = "_blank">Invent8.9_MCsortOE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/56/scoring_guides/391/score_assignments" target = "_blank">Swimming1_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/56/scoring_guides/392/score_assignments" target = "_blank">Swimming2a_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/56/scoring_guides/408/score_assignments" target = "_blank">Titanic1a_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/56/scoring_guides/407/score_assignments" target = "_blank">Titanic1b_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scheduled_activities/36/activities/59/scoring_guides/359/score_assignments" target = "_blank">GPA1_MC  </a>


##### Response choice distributions
* See <a href="https://cr4cradmin.bear-apps.com/answers_reports?scheduled_activities=36" target = "_blank">answers report.  </a> 

```{r setup, include=FALSE}
require(WrightMap)
require(tidyverse)
require(RColorBrewer)
require(knitr)
require(kableExtra)

knitr::opts_chunk$set(echo = TRUE)


#Import ConQuest data
MRC <- CQmodel(p.est = "data/MRC_WLE.txt", show = "data/MRC_SHOW.txt")

#full item names
i.names<-MRC$RMP$item$item
i.names[1,] <- "Swim1_MC"
i.names[2,] <- "Swim2_MC"
i.names[3,] <- "Titanic1b_MC"
i.names[4,] <- "Titanic1a_MC"
i.names[5,] <- "Birthday1_MC"
i.names[6,] <- "GPA1_MC"
i.names[7,] <- "AirQuality1_MC"
i.names[8,] <- "Invent7_MC"
i.names[9,] <- "Invent89_MCsortOE" 
itemnames <- sort(i.names)

#thetas
MRC_est<-MRC$p.est$`est (d1)`

#move thresholds for items that skipped levels (by design)
MRC_thresh <- make.thresholds(MRC) %>% 
  as.data.frame()

# mannually adjusting thresholds for skipped levels etc.

# Swim1 - L1 --> L3
MRC_thresh[1, 3] <- MRC_thresh[1, 1]
MRC_thresh[1, 1] <- NA

# Swim2 - L1 --> L3
MRC_thresh[2, 3] <- MRC_thresh[2, 1]
MRC_thresh[2, 1] <- NA

# get item rownames as the first column
MRC_thresh <- MRC_thresh %>% 
  rownames_to_column(., "item")

MRC_thresh <- MRC_thresh %>% arrange(item)

# get the right item names as set above
MRC_thresh$item <- itemnames

MRC_thresh <- MRC_thresh %>% arrange(item) 
View(MRC_thresh)

# add col names for MRC_thresh df
colnames(MRC_thresh) <- c("item", "L1", "L2 ", "L3", "L4", "L5")

#get rid of item col for WrightMap 1
thresh4wm1 <- MRC_thresh %>% select(-item)


# transposing item_thresh for WM2
library(tidyr)
#transposing item_thresh to tt for Wright map #2 w/thresholds on x-axis   
tt <- MRC_thresh %>%
  gather(var, value, -item) %>% 
  spread(item, value) 
dim(tt) # 5 x 10

# drop the first column
tt <- tt[(1:5), (2:10)]

# x-axis labels for Wright map #2
itemnames2 <- c("L0 vs.L1", "L1 vs.L2", "L2 vs.L3", "L3 vs.L4", "L4 vs.L5")
#colors for Wright map #2
itemcolors <- c("#D7191C", "#2B83BA", "forestgreen", "blueviolet", "orange2")

#color code categories
ncat <- ncol(thresh4wm1)
nitems <- nrow(thresh4wm1)
itemlevelcolors <- matrix(rep( RColorBrewer::brewer.pal(ncat, "Set1"), nitems), byrow=TRUE, ncol=ncat)

```

### 3. Wright Maps

```{r plots, echo=FALSE, results = FALSE, fig.keep = 'all', message = FALSE, warning = FALSE, fig.align = "center"}

#Wright map #1 (items on x-axis)
wrightMap(MRC_est, thresh4wm1,
          label.items = itemnames, 
          label.items.srt = 65, 
          thr.sym.col.fg = itemlevelcolors, 
          thr.sym.col.bg = itemlevelcolors,
          axis.items="")

#mean(MRC$p.est$`est (d1)`)
#sd(MRC$p.est$`est (d1)`)

#Wright map #2 (thresh on x-axis)
wrightMap(MRC_est, tt,
          label.items = itemnames2,
          main.title   = "Wright Map: MRC (by thresholds)",
          thr.sym.col.fg = itemcolors,
          thr.sym.col.bg = itemcolors,
          axis.items = "Threshold")

```

```{r calib.results, echo=FALSE, results = FALSE}
n.cases <- length(MRC_est)
n.items <- length(i.names)
eap.rel <- MRC$rel.coef[[3]]
min.Wfit <- min(MRC$RMP$item$W.fit)
max.Wfit <- max(MRC$RMP$item$W.fit)
```
#####   Calibration stats

*  `r n.cases` cases (the overall DDM sample is 2,265. Of which, 422 are AP Stats students. 28 students excluded due to answering less than 20% of items; 3 more dropped for unknown reason.)
*  `r n.items` scorable "units"
*  EAP/PV Reliability: `r eap.rel`
*  Weighted MNSQ range: `r min.Wfit` - `r max.Wfit`


#####   Observations

* Swim2_MC: The most difficult item. Frequency on the y-axis might be an appealing distractor. Better to be labeled as "number of respondents"?
* Swim1_MC: Very easy as only two options are plausible.
* Invent7's L3 appears to be more like Level 4.
* AirQuality and GPA are parallel items but L2 and L3 locations are somewhat different. 
* Birthday & Invent89 have a nice spread among the thresholds, while Titanic1b's thresholds are all squished. 

### 4. Threshold Difficulty
```{r tables, echo=FALSE, message = FALSE, warning = FALSE}

knitr::kable(MRC_thresh, format = "html", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"),
                full_width = TRUE, font_size = 12)

```

### 5. Item Analysis
* <a href="https://drive.google.com/file/d/1gaKwS-sWlXFbEKZlkMs9fg9ZuFWGvADp/view?usp=sharing" target = "_blank">Link to Item Analysis </a> (ConQuest output)   
