---
title: "DDM_Pre20_UMV"
author: "Aubrey Condor"
date: "3/4/2021"
output:
  html_document: default
  pdf_document: default
---

### 1. UMV (understanding measures of variability) Construct Map
<a href="https://cr4cradmin.bear-apps.com/constructs/public/HxpdvrHpo2zUj65hjNZXyJuheExFSY" target = "_blank">Link </a> to construct map

### 2. Items & Scoring Guides
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/AJKwoSsbWJBhVKPwwLg9hGQWgf65U2" target ="_blank"> CuppaJoe.04_MC </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/YWkAtnwQM7OcCF8l4IRhX1qoME539g" target = "_blank">Inventions.04a_MConly  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/PHKBjKc5CJBtPJ1AvTELIaJgWqVKTT" target = "_blank">Inventions.03ab_MCMC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/farxoPV1WDRsHmybnmOvKLn419noGw" target = "_blank">GuineaPig.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/k8AALCWT3VWtA1J99oqhfkvOIn6t4C" target = "_blank">GuineaPig.03_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/SYBBDTg5AwqNZbbtF3anDA5Xjvjp7c" target = "_blank">GuineaPig.02_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/YYVg87Kjz54mnJHea5jPY872MX68pl" target = "_blank">CuppaJoe.01_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/mJ3YclywhzWzuzwQMxRVL6Mmo9PAYV" target = "_blank">DogDiet.02_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/4iqcjSHmUdaWa5yWVmQ8pDwfERQdJG" target = "_blank">DogDiet.03_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/RLJP4Y6hO72MAfhYb91AdGA3LQS5UH" target = "_blank">Inventions.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/oKLQNB287yJLZ3pRAOoKPSySAc7QK2" target = "_blank">PopSongs.01_MC  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/fxsegyrwwhlmKuy7QEDdY7CBJ33jJM" target = "_blank">PopSongs.01_MCOE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/5u7fKqr9iksqA4FpON3HlueOVsLRQJ" target = "_blank">MMpacket.01ab_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/juP7IVJnOooBS6Ij6qZK6MVicGlpAD" target = "_blank">MMpacket.05  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/WdBVXbKRbnP6rIq2wG2eYvWJaxugJ4" target = "_blank">MMpacket.02ab_NU  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/Z5qxNBXMCyS6hGD3eA7JomNeUenWrc" target = "_blank">MMpacket.03ab_NU  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/ANRqfxKdaNBcLC9RLvMW1621JaxlIW" target = "_blank">MMpacket.04ab_NU  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/8udfxCj6Kmr9Tjd1HVFk9kxXPHP6H8" target = "_blank">CuppaJoe.03_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/KhXIDs9be4s5tQh1zRO39ajvqPCzG1" target = "_blank">Painting.02_OE  </a>
* <a href="https://cr4cradmin.bear-apps.com/scoring_guides/public/iHUxQhsS82uZjjO3iCf1FAVSBWLLyP" target = "_blank">Painting.01_OE  </a>


```{r setup, include=FALSE}
library(TAM)
library(dplyr)
library(WrightMap)
setwd("C:/Users/condo/PycharmProjects/NMSI_stat")

# change file depending on the construct
##############################################################################
raw_resp <- read.csv("R_UMV.csv")
##############################################################################

resp <- raw_resp[!!rowSums(!is.na(raw_resp)),]
resp <- lapply(resp, as.numeric)
resp <- as.data.frame(resp)

mod1 <- tam(resp)
item_param <- mod1$xsi$xsi #item parameters
item_thresh <- tam.threshold(mod1) #thurst thresholds
summary(mod1) # summary of the model

pers_abil <- mod1$person$EAP

item_thresh['CuppaJoe.04_MC', 1] <- NA
item_thresh['GuineaPig.01_MC', 1] <- NA
item_thresh['Inventions.03ab_MCMC', 1] <- NA
item_thresh['Inventions.04a_MConly', 1] <- NA
item_thresh['Inventions.01_MC', 1] <- NA
item_thresh['MMpacket.01ab_OE', 1] <- NA
item_thresh['GuineaPig.02_MC', 1] <- NA
item_thresh['PopSongs.01_MC', 2] <- NA

#View(LDC_thresh)
# add col names for LDC_thresh df
#colnames(item_thresh) <- c("item", "L1", "L2 ", "L3", "L4")
#get rid of item col for WrightMap 1
#thresh4wm1 <- item_thresh %>% select(-item)
# transposing item_thresh for WM2
library(tidyr)
#transposing item_thresh to tt for Wright map #2 w/thresholds on x-axis   
#tt <- item_thresh %>%
#  gather(var, value, -item) %>% 
#  spread(item, value) 
#dim(tt) # 4 x 14
# drop the first column
#tt <- tt[(1:4), (2:14)]
# x-axis labels for Wright map #2
#itemnames2 <- c("L0 vs.L1", "L1 vs.L2", "L2 vs.L3", "L3 vs.L4")
#colors for Wright map #2
#itemcolors <- c("#D7191C", "#2B83BA", "forestgreen", "blueviolet")
#color code categories
#ncat <- ncol(thresh4wm1)
#nitems <- nrow(thresh4wm1)
#itemlevelcolors <- matrix(rep( RColorBrewer::brewer.pal(ncat, "Set1"), nitems), byrow=TRUE, ncol=ncat)
```

### 3. Wright Maps

```{r plots, echo=FALSE, results = FALSE, fig.keep = 'all', message = FALSE, warning = FALSE, fig.align = "center"}
#Wright map #1 (items on x-axis)
library(RColorBrewer)
ncat <- 5
I <- ncol(mod1$resp)
itemlevelcolors <- matrix(rep( RColorBrewer::brewer.pal(ncat, "Set1"), I),
                           byrow=TRUE, ncol=ncat)

wrightMap(pers_abil, item_thresh, thr.sym.col.fg=itemlevelcolors,
          thr.sym.col.bg=itemlevelcolors,label.items.srt=65)
#mean(LDC$p.est$`est (d1)`)
#sd(LDC$p.est$`est (d1)`)
#Wright map #2 (thresh on x-axis)
#wrightMap(item_est, tt,
#          label.items = itemnames2,
#          main.title   = "Wright Map: LDC (by thresholds)",
#          thr.sym.col.fg = itemcolors,
#          thr.sym.col.bg = itemcolors,
#          axis.items = "Threshold")
```

```{r calib.results, echo=FALSE, results = FALSE}
n.cases <- dim(resp)[1]
n.items <- dim(item_thresh)[1]
eap.rel <- mod1$EAP.rel
#min.Wfit <- min(LDC$RMP$item$W.fit)
#max.Wfit <- max(LDC$RMP$item$W.fit)
```
#####   Calibration stats

*  `r n.cases` cases (the overall DDM sample is 2,265. Of which, 422 are AP Stats students. 28 students excluded due to answering less than 20% of items.)
*  `r n.items` scorable "units"
*  EAP/PV Reliability: `r eap.rel`



#####   Observations




